---
title: "GCPtools"
author: "AnVIL Team"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  BiocStyle::html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
package: GCPtools
vignette: >
  %\VignetteIndexEntry{GCPtools Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# GCPtools

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
has_gcloud <- GCPtools::gcloud_exists()
options(width = 75)
```

GCPtools is a package that provides an interface to Google Cloud Platform (GCP)
tools, primarily the `gcloud` and `gsutil` utilities. It allows users to
interact with GCP services such as Google Cloud Storage (GCS) and Google Compute
Engine (GCE) directly from R.

# Installation and Load

You can install the latest version of `GCPtools` from GitHub using the
following:

```
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("Bioconductor/GCPtools")
```

After installation, you can load the package using:

```{r load-gcp-tools,include=TRUE,results="hide",message=FALSE,warning=FALSE}
library(GCPtools)
```

# Usage

The package provides functions to interact with GCP services. For example, you
can use `gcloud_access_token()` to obtain an access token for a specific
service. This is currently in use by `AnVIL` and `AnVILGCP` R packages.

```{r gcloud-access-token,eval=FALSE}
gcloud_access_token("terra")
```

The `gcloud_exists()` function is used to check if the `gcloud` command line
utility is available on your system.

```{r gcloud-exists}
gcloud_exists()
```

The package also includes functions to manage Google Cloud
Storage buckets and objects, such as `gsutil_ls()` to list objects in a bucket
and `gsutil_cp()` to copy files to and from GCS.
